Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-20 paper/aldebaran.tex
history

@@

\section{Aldebaran}

>>>>

Aldebaran, or $\alpha$~Tauri, is one of the brightest and most easily recognized naked-eye stars, and has long been the subject of astronomical investigations. Following the proposal of \citet{struverv} several groups began to search for planets by the radial velocity (RV) method, looking for Doppler shifts from the star's reflex motion around the common centre of mass, culminating in the discovery of 51~Peg~b \citep{51peg}, the first exoplanet to be recognized as such. Before this, \citet{hatzes1993} noted RV variations in Pollux \citep[$\beta$~Gem; subsequently confirmed as a planet:][]{betgemconf,betgemconf2}, Arcturus ($\alpha$~Boo, unconfirmed), and Aldebaran.

@@

\section{Aldebaran}
Aldebaran is one of the nearest red giant stars, at a distance of only $19.96 \pm 0.38$~pc \citep{hipparcos}, and its position near the Ecliptic permits the determination of its angular diameter by lunar occultations and by interferometry \citep[$20.58 \pm 0.03$ mas;][]{richichi2005,1979ApJ...228L.111B,brown1979,panek1980}.
